{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-24 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
conclusions and discussions

\subsection{Redrawing Great Britain's Urban Boundaries}
The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain.
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
It provides an adequate resolution for a country wide investigation~\citep{ratti2010}.
The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
We used this connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
These results are expected given that most of the tweets originate in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance results in different delineations of the catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\citep{simini2012} and the distance decay effect on attracting movers~\citep{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions where no, or few, Twitter users had visited (e.g. forests, agriculture) especially when restricting the analysis to short distance Twitter user displacements.

@@

A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.

The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas, which is explained by the usual flight passenger routes.
The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
For example, East Barnet and West Enfield seem to have higher interactions than those resulted from in the emerging cohesive zone between the two boroughs.

>>>>

\subsection{Redrawing Great Britain's Urban Boundaries}
The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain (see Fig.~\ref{S4_Fig} - c).
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
It provides an adequate resolution for a country wide investigation~\citep{ratti2010}.
The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
We used this connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
These results are expected given that most of the tweets originate in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance results in different delineations of the catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\citep{simini2012} and the distance decay effect on attracting movers~\citep{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions where no, or few, Twitter users had visited (e.g. forests, agriculture) especially when restricting the analysis to short distance Twitter user displacements.

@@

A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
Since the captured Twitter user movements were on intra-city level (in comparison to the national level in Fig.~\ref{S4_Fig}-c), there was no distinct distance range to separate Twitter user spatial coverage in terms of radius of gyration (see Fig.~\ref{S4_Fig}-d). 
We chose 1-km cell size as referred from the related literature~\citep{liu2015}, which suggested 1-km cell size is detailed enough to depict urban structures.
The spatial partitions derived from a fine grid of 1km used all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas, which is explained by the usual flight passenger routes.
The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
For example, East Barnet and West Enfield seem to have higher interactions than those resulted from in the emerging cohesive zone between the two boroughs.
